Evaluating FAIR Digital Object and Linked Data as distributed object systems

### 2023-06-15 latex/main.tex
corporate authors

It's also a question as to whether a highly constrained protocol revolving around persistent identifiers is in fact necessary. For example, DOIs are mostly resolved on the web \autocite{DOIResolutionDocumentation} using HTTP redirects with the common \texttt{https://doi.org/} prefix, hiding their Handle nature as an implementation detail \autocite{DOIHandbookResolution}.

>>>>

It's also a question as to whether a highly constrained protocol revolving around persistent identifiers is in fact necessary. For example, DOIs are mostly resolved on the web \autocite{DOIHandbookResolution} using HTTP redirects with the common \texttt{https://doi.org/} prefix, hiding their Handle nature as an implementation detail \autocite{DOIHandbookResolution}.
